High resolution, annual maps of the characteristics of smallholder-dominated croplands at national scales

### 2021-03-05 inst/manuscript/manuscript.Rmd
Abstract added

documentclass: article
classoption: a4paper
capsize: normalsize
fontsize: 11pt
geometry: margin=1in
linenumbers: yes
spacing: doublespacing
footerdate: yes
abstract:

@@

# Introduction
Amidst all the challenges posed by global change, a particular concern is how agriculture will adapt to meet humanity's growing food demands, and the impacts that a transforming and expanding agriculture will have on societies, economies, and environment [@searchingerCreatingSustainableFood2019]. Significant efforts are being made to address the various aspects of this challenge, including work on diagnosing and closing yield gaps [e.g. @LickerMindgaphow2010; @lobellCropYieldGaps2009; @muellerClosingYieldGaps2012], expanding and commercializing production [@morrisAwakeningAfricaSleeping2009], and to understand [@davisTropicalForestLoss2020; @kehoeNatureRiskFuture2017; @RulliFoodappropriationlarge2014] and mitigate [@EstesReconcilingagriculturecarbon2016] agriculture's ecological impacts. Answering many of the questions these efforts seek to address depends on reliable data that describes the location and characteristics of cropland [@FritzMappingglobalcropland2015], and how these are changing over time. Unfortunately, the data that do exist are in many places inaccurate or missing. Existing estimates of how much cropland there is tend to vary widely, and they often disagree about where cropland is located [e.g. @FritzHighlightingcontinueduncertainty2011; @Fritzneedimprovedmaps2013]. Such errors can propagate in subsequent analyses that rely on cropland data as inputs, resulting in potentially misleading answers [@Esteslargeareaspatiallycontinuous2018]. Beyond cropland distributions, few data are available on cropland characteristics such as field size, which provide important information on agricultural systems  [@lesivEstimatingGlobalDistribution2019]. These inadequacies are due to the fact that cropland data in much of the world are derived from remotely sensed landcover maps, which can be notoriously high in error, particularly over regions such as Africa [@Esteslargeareaspatiallycontinuous2018; @FritzComparisonglobalregional2010], where agricultural changes will be largest and the need for accurate baseline data is thus greatest [@EstesReconcilingagriculturecarbon2016; @SearchingerHighcarbonbiodiversity2015; @bullockThreeDecadesLand2021]

@@

Once the features from the training sites are extracted into `RasterFrames`, these are combined with their corresponding labels and passed to the machine learning classifier, a `SparkMLlib` implementation of Random Forests [@BreimanRandomForests2001]. For this study, the model was trained with a balanced sample and a tree depth of 15 and total tree number of 80, which initial testing showed to provide a reasonable balance between computational time and performance.

>>>>

documentclass: article
classoption: a4paper
capsize: normalsize
fontsize: 11pt
geometry: margin=1in
linenumbers: yes
spacing: doublespacing
footerdate: yes
abstract: Understanding agricultural change requires reliable, frequently updated maps that describe the characteristics of croplands. Such data are often unavailable for regions dominated by smallholder agricultural systems, which are particularly challenging for remote sensing. To overcome these challenges, we designed a system to minimize several sources of error that arise when mapping smallholder croplands. To overcome errors caused by mismatches between image resolution and cropland scales, the system converts daily, 3.7 m PlanetScope imagery into two seasonal composites within a single agricultural year. To reduce errors that occur when training classifiers, we built a labelling platform that rigorously assesses label accuracy, and creates more accurate consensus labels that train a Random Forests model. The labelling platform and model interact within an active learning process that boosts the accuracy of the resulting cropland probability map, which combines with a segmentation process to delineate individual field boundaries. We applied this system to map Ghana’s croplands for the year 2018. We divided Ghana into 16 mapping regions (12,160-23,535 km$^2$), training separate models for each using a total of 6,299 labels, plus 1,600 for validation. Using an independent map reference sample (n=1,207), we found that overall accuracies of the resulting cropland probability and field boundary maps were 88% and 86.7%, respectively, with User’s accuracies for the cropland class of 61.2% and 78.9%, and Producer’s accuracies of 67.3% and 58.2%. Croplands covered 16.1-23.2% of the mapped area, comprising 1,131,146 total fields with an average size of 3.92 ha. Unbiased estimates based on the map reference sample yield indicate a cropland percentage of 17.1% (15.4-18.9%) or 17.6% (15.6-19.6%), depending on whether the cropland probability or field boundary map was assessed. Using the labellers’ digitized field boundaries to estimate biases in field boundary statistics, we calculated an adjusted mean field size of 1.73 ha and total field count of 1,662,281. Although the cropland class contained substantial errors, the system was effective in mitigating error and quantifying resulting performance gains. By minimizing training errors, consensus labelling improved the model’s F1 scores by up to 25%, while 3 iterations of active learning increased the F1 score by 9.1%, on average, which was 2.3% higher than training models with randomly selected labels. Map accuracy may be further improved by replacing Random Forests with a convolutional neural network. These results demonstrate a readily adapted, transferrable framework for developing high resolution, annual, nation-scale maps that provide important details about smallholder-dominated croplands.

@@

# Introduction
Amidst all the challenges posed by global change, a particular concern is how agricultural systems will adapt to meet humanity's growing food demands, and the impacts that transforming and expanding food systems will have on societies, economies, and the environment [@searchingerCreatingSustainableFood2019]. Significant efforts are being made to address the various aspects of this challenge, including work on diagnosing and closing yield gaps [e.g. @LickerMindgaphow2010; @lobellCropYieldGaps2009; @muellerClosingYieldGaps2012], expanding and commercializing production [@morrisAwakeningAfricaSleeping2009], and to understand [@davisTropicalForestLoss2020; @kehoeNatureRiskFuture2017; @RulliFoodappropriationlarge2014] and mitigate [@EstesReconcilingagriculturecarbon2016] agriculture's ecological impacts. Answering many of the questions these efforts seek to address depends on reliable data that describes the location and characteristics of cropland [@FritzMappingglobalcropland2015], and how these are changing over time. Unfortunately, the data that do exist are in many places inaccurate or missing. Existing estimates of how much global cropland there is tend to vary widely, and they often disagree about where cropland is located [e.g. @FritzHighlightingcontinueduncertainty2011; @Fritzneedimprovedmaps2013]. Such errors can propagate in subsequent analyses that rely on cropland data as inputs, resulting in potentially misleading answers [@Esteslargeareaspatiallycontinuous2018]. Beyond cropland distributions, few data are available on cropland characteristics such as field size, which provide important information on agricultural systems  [@lesivEstimatingGlobalDistribution2019]. These inadequacies are due to the fact that cropland data in much of the world are derived from remotely sensed landcover maps, which can be notoriously high in error, particularly over regions such as Africa [@Esteslargeareaspatiallycontinuous2018; @FritzComparisonglobalregional2010], where agricultural changes will be largest and the need for accurate baseline data is thus greatest [@EstesReconcilingagriculturecarbon2016; @SearchingerHighcarbonbiodiversity2015; @bullockThreeDecadesLand2021]

@@

Once the features from the training sites are extracted into `RasterFrames`, these are combined with their corresponding labels and passed to the machine learning classifier, a `SparkMLlib` implementation of Random Forests [@BreimanRandomForests2001]. For this study, the model was trained with a balanced sample and a tree depth of 15 and total tree number of 60, which initial testing showed to provide a reasonable balance between computational time and performance.
